Quasicharacters and the function-sheaf dictionary

### 2014-09-08 crelle-dictionary.tex
Hardwired bibliography, with Crelle sample

%%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%
% Encodings
%\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
% AMS packages
%\usepackage{amsmath, amsthm, amssymb}
\usepackage{todonotes}%, showkeys}
\usepackage{amsrefs}
% Fonts
\usepackage{mathrsfs, yfonts}
%Geometry
%\usepackage{geometry}
% Enumitem
\usepackage{enumitem}
% TikZ
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,calc,matrix}
\usepackage{tikz-cd}
% Hyperrefs
\usepackage{hyperref}

@@

\DeclareMathOperator{\Pic}{Pic}

@@

\newcommand{\latop}[2]{\genfrac{}{}{0pt}{0}{#1}{#2}}
\newcommand{\partop}[2]{\genfrac{(}{)}{0pt}{0}{#1}{#2}}

@@

\newcommand\Clifton[1]{\marginpar{\smaller\smaller CC: #1}}
\newcommand\David[1]{\marginpar{\smaller\smaller DR: #1}}

@@

Let $K$ be a local field with finite residue field $\Fq$. 
In this section we consider connected commutative algebraic groups over $K$ that admit a N\'eron model, by which we mean a locally finite type N\'eron model.
By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected commutative algebraic groups over $K$ that contain no subgroup isomorphic to $\mathbb{G}_\text{a}$.
Write $\mathcal{N}_K$ for the full subcategory of the category of algebraic groups consisting of such objects.  This category is additive, and includes all algebraic tori over $K$, abelian varieties over $K$ and unipotent $K$-wound groups.

@@

\begin{theorem}\label{thm:QCXK}
Let $K$ and $R$ be as above. 
\begin{enumerate}
\item
The trace of Frobenius provides a natural transformation between the additive functors
\[
F_{\QC}: X_K \mapsto \QCiso{X_K}
\qquad\text{and}\qquad
F_{\text{qc}}: X_K \mapsto \Hom_{\text{qc}}(X(K),\EEx)
\]
as functors from $\mathcal{N}_K$ to the category of abelian groups.
\end{enumerate} 
Regarding this natural transformation, for every $X_K \in \mathcal{N}_K$ with N\'eron model $X$:
\begin{enumerate}[resume]
\item there is a canonical short exact sequence of abelian groups 
\[
0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{}} \to \QCiso{X_K} \to \Hom_\text{qc}(X(K),\EEx) \to 0;
\] 
\item for all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
\item for all quasicharacter sheaves $\qcs{F}$ for $X_K$, there is a canonical isomorphism
\[
\Aut(\qcs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx).
\]
\end{enumerate}
\end{theorem}

@@

%-------------------------------------------------------------------------%
% BIBLIOGRAPHY                                                            %
% References should be collected at the end of the paper and numbered in  %
% alphabetical order of the authors' names. Titles of journals should be  %
% abbreviated as in Mathematical Reviews. Please do not use small caps    %
% for the names of the authors. The preferred style is shown in the       %
% examples below.                                                         %
% Refer to the bibliography entries using \cite commands.                 %
% Using BibTeX, you simply have to add the names of your databases as     %
%   \bibliography{mydatabase}                                             %
% The file crelle.bst then ensures the correct style.                     %
%-------------------------------------------------------------------------%
%\bibliographystyle{amsalpha}
\bibliography{../bibliography/Biblio}

>>>>

%%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%
% Encodings
%\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
% AMS packages
%\usepackage{amsmath, amsthm, amssymb}
\usepackage{todonotes}%, showkeys}
\usepackage{amsrefs}
\BibSpec{lecture}{%
  +{}{\PrintAuthors} {author}
  +{,}{ \textit} {title}
  +{}{ \parenthesize} {date}
  +{,}{ } {note}
  +{,}{ } {location}
  +{.}{ } {transition}
}
\BibSpec{preprint}{%
  +{}{\PrintAuthors} {author}
  +{,}{ \textit} {title}
  +{,}{ preprint } {date}
  +{,}{ } {note}
  +{.}{ } {transition}
}
% Fonts
\usepackage{mathrsfs, yfonts}
%Geometry
%\usepackage{geometry}
% Enumitem
\usepackage{enumitem}
% TikZ
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,calc,matrix}
\usepackage{tikz-cd}
% Hyperrefs
\usepackage{hyperref}

@@

%\DeclareMathOperator{\Pic}{Pic}

@@

%\newcommand{\latop}[2]{\genfrac{}{}{0pt}{0}{#1}{#2}}
%\newcommand{\partop}[2]{\genfrac{(}{)}{0pt}{0}{#1}{#2}}

@@

%\newcommand\Clifton[1]{\marginpar{\smaller\smaller CC: #1}}
%\newcommand\David[1]{\marginpar{\smaller\smaller DR: #1}}

@@

Let $K$ be a local field with finite residue field $\Fq$;
 we continue to assume that $\ell$ is invertible in $\Fq$.
In this section we consider connected commutative algebraic groups over $K$ that admit a N\'eron model, by which we mean a locally finite type N\'eron model.
By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected commutative algebraic groups over $K$ that contain no subgroup isomorphic to $\mathbb{G}_\text{a}$.
Write $\mathcal{N}_K$ for the full subcategory of the category of algebraic groups consisting of such objects.  This category is additive, and includes all algebraic tori over $K$, abelian varieties over $K$ and unipotent $K$-wound groups.

@@

\begin{theorem}\label{thm:QCXK}
Let $K$ be a local field with residue field $\Fq$, in which $\ell$ is invertible; 
let $R$ be the ring of integers of $K$.
\begin{enumerate}
\item
The trace of Frobenius provides a natural transformation between the additive functors
\[
F_{\QC}: X_K \mapsto \QCiso{X_K}
\qquad\text{and}\qquad
F_{\text{qc}}: X_K \mapsto \Hom_{\text{qc}}(X(K),\EEx)
\]
as functors from $\mathcal{N}_K$ to the category of abelian groups.
\end{enumerate} 
Regarding this natural transformation, for every $X_K \in \mathcal{N}_K$ with N\'eron model $X$:
\begin{enumerate}[resume]
\item there is a canonical short exact sequence of abelian groups 
\[
0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{}} \to \QCiso{X_K} \to \Hom_\text{qc}(X(K),\EEx) \to 0;
\] 
\item for all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
\item for all quasicharacter sheaves $\qcs{F}$ for $X_K$, there is a canonical isomorphism
\[
\Aut(\qcs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx).
\]
\end{enumerate}
\end{theorem}

@@

%-------------------------------------------------------------------------%
% BIBLIOGRAPHY                                                            %
% References should be collected at the end of the paper and numbered in  %
% alphabetical order of the authors' names. Titles of journals should be  %
% abbreviated as in Mathematical Reviews. Please do not use small caps    %
% for the names of the authors. The preferred style is shown in the       %
% examples below.                                                         %
% Refer to the bibliography entries using \cite commands.                 %
% Using BibTeX, you simply have to add the names of your databases as     %
%   \bibliography{mydatabase}                                             %
% The file crelle.bst then ensures the correct style.                     %
%-------------------------------------------------------------------------%
%\bibliographystyle{amsalpha}
%\bibliography{../bibliography/Biblio}

\begin{bibdiv}
\begin{biblist}
%\bibselect{references}

\bib{beilinson-bernstein-deligne:81a}{article}{
   author={\it A. A. Be{\u\i}linson},
   author={\it J. Bernstein},
   author={\it P. Deligne},
   title={\rm Faisceaux pervers},
   journal ={Ast\'erisque},
   volume={100},
   publisher={Soc. Math. France},
   place={Paris},
   date={1982},
   pages={5--171},
%conference={
%      title={Analyse et topologie sur les espaces singuliers, I},
%      address={Luminy},
%      date={1981},
%   }
}

\bib{bernstein:vogan_conference}{lecture}{
	author = {\it J. Bernstein},
	title = {\rm Stacks in Representation Theory: What is a representation of an algebraic group?},
 note={Lecture delivered at {\it A conference dedicated to David Vogan on his 60th birthday: Representations of reductive groups}, \url{http://math.mit.edu/conferences/Vogan/}},
 	date={May, 2014},
 	location={MIT, Boston},
 }

 \bib{bernstein-luntz:equivariant_sheaves}{book}{
      author={\it J. Bernstein},
      author={\it V. Luntz},
       title={\rm Equivariant sheaves and functors},
      series={Lecture Notes in Mathematics},
   publisher={Springer-Verlag},
     address={Berlin},
        date={1994},
      volume={1578},
}

\bib{bertrapelle-gonzales:Greenberg}{preprint}{
      author={\it A. Bertrapelle},
      author={\it C.-D. Gonz\'ales-Avil\'es},
       title={\rm The Greenberg functor revisited},
        note={\url{arXiv:1311.0051v1}},
      date={2013},
}

\bib{bitan:discriminant}{article}{
      author={\it R. A. Bitan},
       title={\rm The discriminant of an algebraic torus},
        date={2011},
     journal={J. Number Theory},
      volume={131},
      number={9},
       pages={1657\ndash 1671},
}

\bib{bosch-lutkebohmert-reynaud:NeronModels}{book}{
      author={\it S. Bosch},
      author={\it W. L\"utkebohmert},
      author={\it M. Reynaud},
       title={\rm N\'eron models},
   publisher={Springer-Verlag},
     address={Berlin},
        date={1980},
}

\bib{brown:CohomologyGrps}{book}{
      author={\it K. S. Brown},
       title={\rm Cohomology of groups},
      series={Graduate Texts in Mathematics 87},
   publisher={{Springer-Verlag}},
     address={New York},
        date={1982},
}

\bib{cartan-eilenberg:HomologicalAlgebra}{book}{
      author={\it H. Cartan},
      author={\it S. Eilenberg},
       title={\rm Homological algebra},
   publisher={Princeton U.P.},
     address={Princeton},
        date={1956},
}

\bib{cassels-frohlich:AlgebraicNumberTheory}{book}{
      editor={\it J. W. S. Cassels},
      editor={\it A. Frohlich},
       title={\rm Algebraic number theory},
     edition={2nd ed.,},
   publisher={London Math Society},
     address={London},
        date={2010},
}

\bib{chai-yu:01a}{article}{
      author={\it C.-L. Chai},
      author={\it J.-K. Yu},
       title={\rm Congruences of N\'eron models for tori and the Artin
  conductor},
        date={2001},
     journal={Annals of Math},
      volume={154},
      number={2},
       pages={347\ndash 382},
}

\bib{deligne:SGA4.5}{book}{
      author={\it P. Deligne},
       title={\rm Cohomologie \'Etale},
      series={{Lecture Notes in Mathematics 569}},
   publisher={{Springer-Verlag}},
     address={Berlin},
        date={1977},
}

\bib{deligne:80a}{article}{
      author={\it P. Deligne},
       title={\rm La conjecture de Weil II},
        date={1980},
     journal={{Inst. Hautes \'Etudes Sci. Publ. Math.}},
      volume={52},
       pages={137\ndash 252},
}

\bib{deligne:02a}{article}{
      author={\it P. Deligne},
       title={\rm {Cat\'egories tensorielles}},
        date={2002},
     journal={{Mosc. Math. J.}},
      volume={2},
      number={2},
       pages={227\ndash 248},
}

\bib{deligne-katz:SGA7.2}{book}{
      author={\it P. Deligne},
      author={\it N. Katz},
       title={\rm {Groupes de monodromie en g\'eom\'etrie alg\'ebrique. II}},
      series={{Lecture Notes in Mathematics}},
   publisher={{Springer-Verlag}},
     address={Berlin},
        date={1973},
      volume={340},
}

\bib{demazure-gabriel:GroupesAlgebriques}{book}{
      author={\it M. Demazure},
      author={\it P. Gabriel},
       title={\rm {Groupes alg\'ebriques. Tome 1: G\'eom\'etrie alg\'ebrique,
  g\'en\'eralit\'es, groupes commutatifs}},
   publisher={{Masson \& Cie}},
     address={Paris},
        date={1970},
        note={(Appendix: {\it M. Hazewinkel}, Corps de classes local)},
}

\bib{etingof:09a}{unpublished}{
      author={\it P. Etingof},
      author={\it S. Gelaki},
      author={\it D. Nikshych},
      author={\it V. Ostrik},
       title={\rm Tensor categories},
        date={2009},
        note={{Lecture notes for MIT's 18.769}, \url{www-math.mit.edu/~etingof/tenscat.pdf}},
}

\bib{vdGeer-Moonen:AbelianVarieties}{preprint}{
      author={\it G. van der Geer},
      author={\it B. Moonen},
       title={\rm {Abelian varieties}},
        date={2013},
       note={\url{http://staff.science.uva.nl/~bmoonen/boek/BookAV.html}},
%        note={Writing in progress.},
}

\bib{greenberg:61}{article}{
      author={\it M. J. Greenberg},
       title={\rm {Schemata over local rings I}},
        date={1961},
     journal={Annals of Math},
      volume={73},
      number={2},
       pages={624\ndash 648},
}

\bib{greenberg:63a}{article}{
      author={\it M. J. Greenberg},
       title={\rm {Schemata over local rings II}},
        date={1963},
     journal={Annals of Math},
      volume={78},
      number={2},
       pages={256\ndash 266},
}

\bib{EGAIV2}{article}{
      author={\it A. Grothendieck},
       title={\rm {\'El\'ements de g\'eom\'etrie alg\'ebrique. IV. \'Etude locale
  des sch\'emas et des morphismes de sch\'emas. II}},
        date={1965},
     journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
      number={24},
}

\bib{SGA5}{book}{
      author={\it A. Grothendieck},
       title={\rm {S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois Marie 1965--66
  SGA5: Cohomologie $\ell$-adique et Fonctions L}},
      series={{Lecture Notes in Mathematics}},
   publisher={{Springer-Verlag}},
        date={1977},
      volume={589},
}

\bib{kamgarpour:09a}{article}{
      author={\it M. Kamgarpour},
       title={\rm {Stacky abelianization of algebraic groups}},
        date={2009},
     journal={{Transform. Groups}},
      volume={14},
      number={4},
       pages={825\ndash 846},
}

\bib{lang:56a}{article}{
      author={\it S. Lang},
       title={\rm{Algebraic groups over finite fields}},
        date={1956},
     journal={Amer. J. Math.},
      volume={78},
       pages={555\ndash 563},
}

\bib{laumon:87a}{article}{
      author={\it G. Laumon},
       title={\rm{Transformation de Fourier, constantes d'\'equations
  fonctionnelles et conjecture de Weil}},
        date={1987},
     journal={{Inst. Hautes \'Etudes Sci. Publ. Math.}},
      volume={65},
       pages={131\ndash 210},
}

\bib{lusztig:85a}{article}{
      author={\it G. Lusztig},
       title={\rm {Character Sheaves, I}},
        date={1985},
     journal={Advances in Math.},
      volume={56},
       pages={193\ndash 237},
}

\bib{lusztig:disconnected1}{article}{
      author={\it G. Lusztig},
       title={\rm {Character sheaves on disconnected groups. I}},
        date={2003},
     journal={Representation Theory},
      volume={7},
       pages={374\ndash 403},
}

\bib{nicaise-sebag:motivicSerre}{article}{
      author={\it J. Sebag},
      author={\it N. Nicaise},
       title={\rm{Motivic Serre invariants and Weil restriction}},
        date={2008},
     journal={J. Algebra},
      volume={319},
      number={4},
       pages={1585\ndash 1610},
}

\bib{stacks-project}{misc}{
      author={\it {The {Stacks Project Authors}}},
       title={\rm {Stacks Project}},
        date={2013},
        note={\url{http://stacks.math.columbia.edu}},
}

\bib{Vakil:spectral_sequences}{unpublished}{
      author={\it R. Vakil},
       title={\rm{Spectral sequences: friend or foe?}},
        date={2008},
        note={\url{http://math.stanford.edu/~vakil/0708-216/216ss.pdf}},
}

\bib{vogan:93a}{article}{
      author={\it D. Vogan},
       title={\rm {The local Langlands conjecture}},
        date={1993},
     journal={Representation Theory of Groups and Algebras},
      volume={145},
}

\bib{Weibel:Homological_Algebra}{book}{
      author={\it C. A. Weibel},
       title={\rm{An introduction to homological algebra}},
      series={Cambridge Studies in Advanced Mathematics},
   publisher={Cambridge Univ. Press},
     address={Cambridge},
        date={1994},
      volume={38},
}

\end{biblist}
\end{bibdiv}

\begin{thebibliography}{9}

\bibitem{article}
\textit{T.~Angel} and \textit{I.~E.~Shparlinski},
Article in a journal, J. reine angew. Math. \textbf{647} (2010), 123--156.

\bibitem{preprint}
\textit{C.~Bonnaf\'e},
Preprint, preprint 2008, \url{http://arxiv.org/abs/0805.4100}.

\bibitem{proceedings}
\textit{P. Brooksbank},
Article in a conference proceedings,
in: Finite geometries (Pingree Park 2004), Oxford University Press, Oxford (2006), 1--16.

\bibitem{phdthesis}
\textit{J.~D.~King},
Unpublished dissertation,
Ph.D. thesis, University of Cambridge, 1995.

\bibitem{book}
\textit{F. Sukochev}, \textit{S. Lord} and \textit{D. Zanin},
Book, 2nd ed., De Gruyter, Berlin 2012.

\end{thebibliography}
